---
title: "Auto MPG"
author: "Nishval Patel"
date: "4th December 2019"
output: html_document
---

```{r data, echo=FALSE}
### Just change your working directory ###
auto_mpg <- read.csv("auto_mpg.csv")
auto_mpg <- as.data.frame(auto_mpg)

auto_mpg$orogin <- (gsub(2, '0', auto_mpg$orogin))
auto_mpg$orogin <- (gsub(3, '0', auto_mpg$orogin))
auto_mpg$orogin <- as.numeric(auto_mpg$orogin)
auto_mpg$cylinders <- as.numeric(auto_mpg$cylinders)
auto_mpg$horsepower <- as.numeric(auto_mpg$horsepower)
auto_mpg$model_year <- as.numeric(auto_mpg$model_year)
```

## Insight from tree

The main split is displacement. Cylinders are not considered in the tree.

```{r tree, echo=FALSE}
library(rpart)
library(rpart.plot)

auto_tree <- rpart(orogin~ horsepower+cylinders+displacement+acceleration, data=auto_mpg, method="class")
rpart.plot(auto_tree)
```

## Insight from Logistic Model

Cylinder is a significant variable in the model. With every 1 unit increase in cylinder, the odds of success, car being from USA decrease by approx 70%

```{r logit, echo=FALSE}
auto_logit <- glm(orogin ~ horsepower+cylinders+displacement+acceleration, data=auto_mpg, family="binomial")
summary(auto_logit)
```

## Performance Comparision

Red is the tree and Black is the Logistic Model.

The tree is the better fit as it has more area under the curve.

```{r perf, echo=FALSE, message=FALSE}
library(ROCR)
predict_auto_logit <- predict(auto_logit,auto_mpg,type="response")
predict_auto_tree <- predict(auto_tree,auto_mpg,type="prob")

pred_auto_tree <- prediction(predict_auto_tree[,2], auto_mpg$orogin)
pred_auto_logit <- prediction(predict_auto_logit,auto_mpg$orogin)

perf_auto_tree <- performance(pred_auto_tree, "tpr", "fpr")
perf_auto_logit <- performance(pred_auto_logit, "tpr","fpr")

plot(perf_auto_tree, col="red")
plot(perf_auto_logit, col="black", add=TRUE)
```

## AUC

The area under the curve :
Logistic : 94.2%
Tree : 97.8%

```{r auc, echo=FALSE}
auc_tree <- performance(pred_auto_tree, measure = 'auc')
auc_tree <- auc_tree@y.values[[1]]
auc_tree

auc_logit <- performance(pred_auto_logit, measure = 'auc')
auc_logit <- auc_logit@y.values[[1]]
auc_logit
```